Classification of ordinal data in deep learning: an experimental study

### 2019-02-06 paper/ieee.tex
Paper update

	Ordinal classification problems are those where labels are ordered, and there are different inter-classes weights for each pair of classes. This kind of problem can be treated as a nominal classification problem, but when you do this, you are the discarding ordinal information. A better approach is to use specific methods that take into account this kind of information to improve the performance of the classification model. One way to use the ordinal information is to evaluate the model using an ordinal metric. Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics, mehdiyev2016evaluating}. Kappa index is a well-known statistic coefficient defined by Cohen \cite{cohen1960coefficient} to measure inter-rater agreement on classifying elements into a set of categories. Later, Weighted Kappa (WK) is a modified version of the Kappa statistic calculated to allow assigning different weights to different levels of aggregation between two variables. weighted kappa loss was described in previous work~\cite{de2018weighted} and is a cost function that is based on the WK metric. These functions are indicated for problems where different inter-classes weights are assigned, and that work proved that using these functions improves the model performance and reduce the overfitting risk. This kind of problems is associated with ordinal data processing. Those weights are predefined and depend on the type of the chosen WK. In a linear penalization, the weight is proportional to the distance between the predicted and the real class. In the Quadratic Weighted Kappa (QWK) the penalization is proportional to the square of the distance. In this work, we will combine the QWK metric and the QWK loss.

@@

	This paper is organised as follows: in Section~\ref{sect:relatedwork}, we take a look at previous works related to this paper, in Section~\ref{sect:experiments} we describe the model, the experiments and the datasets used, in Section~\ref{sect:results} we present the results obtained and the statistical analysis and finally in Section~\ref{sect:conclusions} we expose the conclusions of this work.

@@

@@

	\begin{itemize}
		\item \textit{Diabetic Retinopathy (DR)}\footnote{https://www.kaggle.com/c/diabetic-retinopathy-detection/data}. DR is a dataset consisting of extremely high-resolution fundus image data. The training set consists of $17563$ pairs of images (where a  pair consists of a left and right eye image corresponding to a patient). In this dataset, we try and predict from five levels of diabetic retinopathy: no DR ($25810$ images), mild DR ($2443$ images), moderate DR ($5292$ images), severe DR ($873$ images), or proliferative DR ($708$ images). The images are taken in variable conditions: by different cameras,  varying conditions of illumination and different resolutions. These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition that was hosted on the Kaggle platform. Also, this dataset was used in later works~\cite{de2018weighted, nebot2016diabetic} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve better performance. A validation set is set aside, consisting of $10\%$ of the patients in the training set. The images are resized to 128 by 128 pixels. Data augmentation techniques are applied to achieve a higher number of samples.

@@

	Both datasets have been artificially equalised using data augmentation techniques~\cite{van2001art, krizhevsky2012imagenet} based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations. In the case of Diabetic Retinopathy Detection, the epoch size has been fixed to $100000$ images per epoch. For the Adience dataset, epoch size is the number of images in the training set.

@@

@@

	\begin{itemize}
		\item \textit{Learning rate}. Learning rate is one of the most critical hyper-parameters to tune for training deep neural networks. Optimal learning rate can vary depending on the dataset and the CNN architecture. Previous works have presented some techniques that adjust this parameter in order to achieve better performance~\cite{smith2017cyclical, senior2013empirical}. Within this work, we have considered three different values for this parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
		\item \textit{Batch size}. Batch size is also an important parameter as it controls the number of weight updates that are made on every epoch. It can affect the training time and the model performance. In this paper, we have tried three separate batch sizes: $5$, $10$ and $15$.
		\item \textit{Link function}. Different link functions have been used for the POM at the last layer output: logit, probit and complementary log-log.
	\end{itemize}

	\section{Results}
	\label{sect:results}
	In this section, we present the results of the experiments. For each dataset, we show a table with the detailed experiments done training the model with each combination of parameters. Every parameter combination has been run five times. These tables show the average quadratic weighted kappa across these five executions for validation and test values.

@@

	\begin{table}[!t]
		\caption{Diabetic Retinopathy results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
		\label{table:DRresults}
		\footnotesize
		\centering
		\begin{tabular}{ccc|cc}
			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline
			$5$ & $10^{-2}$ & Logit & $0.44888$ & $0.41630$\\
			& & Probit & $0.46724$ & $0.45972$\\
			& & c log-log & $0.42854$ & $0.41448$\\
			& $10^{-3}$ & Logit & $0.56496$ & $0.55356$\\
			& & Probit & $0.57084$ & $0.56392$\\
			& & c log-log & $0.54796$ & $0.53436$\\
			& $10^{-4}$ & Logit & $0.52884$ & $0.52032$\\
			& & Probit & $0.53802$ & $0.52302$\\
			& & c log-log & $0.53824$ & $0.51974$\\
			$10$ & $10^{-2}$ & Logit & $0.54970$ & $0.53142$\\
			& & Probit & $0.52124$ & $0.50806$\\
			& & c log-log & $0.42760$ & $0.42270$\\
			& $10^{-3}$ & Logit & $0.58036$ & $0.57686$\\
			& & Probit & $0.56536$ & $0.55810$\\
			& & c log-log & $\textbf{0.58830}$ & $\textbf{0.58150}$\\
			& $10^{-4}$ & Logit & $0.53158$ & $0.53850$\\
			& & Probit & $0.54560$ & $0.54082$\\
			& & c log-log & $0.53928$ & $0.53742$\\
			$15$ & $10^{-2}$ & Logit & $0.55828$ & $0.55076$\\
			& & Probit & $0.54112$ & $0.53430$\\
			& & c log-log & $0.56676$ & $0.56428$\\
			& $10^{-3}$ & Logit & $0.55748$ & $0.55106$\\
			& & Probit & $0.58182$ & $0.57894$\\
			& & c log-log & $0.56340$ & $0.55938$\\
			& $10^{-4}$ & Logit & $0.54686$ & $0.54342$\\
			& & Probit & $0.53258$ & $0.53278$\\
			& & c log-log & $0.53900$ & $0.53828$
		\end{tabular}
	\end{table}

@@

	\subsection{Adience}
	\label{sect:adience}
	Results for the experiments made with the Adience dataset are shown in Table \ref{table:Adienceresults}.

	\begin{table}[!t]
		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
		\label{table:Adienceresults}
		\footnotesize
		\centering
		\begin{tabular}{ccc|cc}
			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline
			$5$ & $10^{-2}$ & Logit & $0.72072$ & $0.68408$\\
			& & Probit & $0.77608$ & $0.72574$\\
			& & c log-log & $0.75430$ & $0.70742$\\
			& $10^{-3}$ & Logit & $0.71460$ & $0.67868$\\
			& & Probit & $0.81906$ & $0.77154$\\
			& & c log-log & $0.57196$ & $0.55608$\\
			& $10^{-4}$ & Logit & $0.54432$ & $0.51934$\\
			& & Probit & $0.54360$ & $0.52422$\\
			& & c log-log & $0.54802$ & $0.52484$\\
			$10$ & $10^{-2}$ & Logit & $0.78872$ & $0.72994$\\
			& & Probit & $0.79332$ & $0.74750$\\
			& & c log-log & $0.78004$ & $0.73260$\\
			& $10^{-3}$ & Logit & $0.49686$ & $0.47112$\\
			& & Probit & $0.59778$ & $0.58476$\\
			& & c log-log & $0.52016$ & $0.49968$\\
			& $10^{-4}$ & Logit & $0.60972$ & $0.56814$\\
			& & Probit & $0.54638$ & $0.52632$\\
			& & c log-log & $0.75428$ & $0.52094$\\
			$15$ & $10^{-2}$ & Logit & $0.79104$ & $0.74388$\\
			& & Probit & $\textbf{0.84254}$ & $\textbf{0.78666}$\\
			& & c log-log & $0.78802$ & $0.74624$\\
			& $10^{-3}$ & Logit & $0.56946$ & $0.52978$\\
			& & Probit & $0.70262$ & $0.65416$\\
			& & c log-log & $0.49242$ & $0.47320$\\
			& $10^{-4}$ & Logit & $0.55202$ & $0.52484$\\
			& & Probit & $0.54288$ & $0.51740$\\
			& & c log-log & $0.53826$ & $0.52542$
		\end{tabular}

	\end{table}

>>>>

	Ordinal classification problems are those where labels are ordered, and there are different inter-classes weights for each pair of classes. This kind of problem can be treated as a nominal classification problem, but when you do this, you are the discarding ordinal information. A better approach is to use specific methods that take into account this kind of information to improve the performance of the classification model. One way to use the ordinal information is to evaluate the model using an ordinal metric. Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics, mehdiyev2016evaluating}. Kappa index is a well-known statistic coefficient defined by Cohen \cite{cohen1960coefficient} to measure inter-rater agreement on classifying elements into a set of categories. Later, Weighted Kappa (WK) is a modified version of the Kappa statistic calculated to allow assigning different weights to different levels of aggregation between two variables. Weighted kappa loss was described in previous work~\cite{de2018weighted} and is a cost function that is based on the WK metric. These functions are indicated for problems where different inter-classes weights are assigned, and that work proved that using these functions improves the model performance and reduce the overfitting risk. This kind of problems is associated with ordinal data processing. Those weights are predefined and depend on the type of the chosen WK. In a linear penalization, the weight is proportional to the distance between the predicted and the real class. In the Quadratic Weighted Kappa (QWK) the penalization is proportional to the square of the distance. In this work, we will combine the QWK metric and the QWK loss.

@@

	This paper is organized as follows: in Section~\ref{sect:relatedwork}, we take a look at previous works related to this paper. Sections~\ref{sect:ordinalproblem} and \ref{sect:pom} present a formal description of an ordinal problem and the Proportional Odds Model. In Section~\ref{sect:experiments} we describe the model, the experiments and the datasets used, in Section~\ref{sect:results} we present the results obtained and the statistical analysis and finally in Section~\ref{sect:conclusions} we expose the conclusions of this work.

@@

	Adience dataset has been used in other works for human age estimation. E. Eidinger \cite{eidinger2014age} presented an approach using support vector machines and neural networks. J.-C. Chen \cite{chen2016cascaded} proposed a coarse-to-fine strategy for deep convolutional networks. G. Levi \cite{levi2015age} presented another convolutional network model for age estimation.

@@

	\begin{itemize}
		\item \textit{Diabetic Retinopathy (DR)}\footnote{https://www.kaggle.com/c/diabetic-retinopathy-detection/data}. DR is a dataset consisting of extremely high-resolution fundus image data. The training set consists of $17563$ pairs of images (where a  pair consists of a left and right eye image corresponding to a patient). In this dataset, we try and predict from five levels of diabetic retinopathy: no DR ($25810$ images), mild DR ($2443$ images), moderate DR ($5292$ images), severe DR ($873$ images), or proliferative DR ($708$ images). The images are taken in variable conditions: by different cameras,  varying conditions of illumination and different resolutions. These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition that was hosted on the Kaggle platform. Also, this dataset was used in later works~\cite{de2018weighted, nebot2016diabetic} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve better performance. A validation set is set aside, consisting of $10\%$ of the patients in the training set. The images are resized to 128 by 128 pixels and rescaled to $[0,1]$ range. Data augmentation techniques are applied to achieve a higher number of samples.

@@

	Both datasets have been artificially equalized using data augmentation techniques~\cite{van2001art, krizhevsky2012imagenet}. However, different transformations were applied to each one. Diabetic Retinopathy dataset augmentation was based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations. Horizontal flipping was the only transformation applied to Adience dataset.

	In the case of Diabetic Retinopathy Detection, the epoch size has been fixed to $100000$ images per epoch. For the Adience dataset, epoch size is the number of images in the training set.

@@

	Also, other evaluation metrics have been used to ease the comparison with other works: Minimum Sensitivity (MS), Mean Absolute Error (MAE), Mean Squared Error (MSE), Correct Classification Rate (CCR), Top-2 CCR, Top-3 CCR and 1-off accuracy.

@@

	\begin{itemize}
		\item \textit{Learning rate}. Learning rate is one of the most critical hyper-parameters to tune for training deep neural networks. Optimal learning rate can vary depending on the dataset and the CNN architecture. Previous works have presented some techniques that adjust this parameter in order to achieve better performance~\cite{smith2017cyclical, senior2013empirical}. Within this work, we have considered three different values for this parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
		\item \textit{Batch size}. Batch size is also an important parameter as it controls the number of weight updates that are made on every epoch. It can affect the training time and the model performance. In this paper, we have tried three separate batch sizes for each dataset. For DR dataset, we have used $5$, $10$ and $15$ while, for the Adience dataset, $64$, $128$ and $256$ was used. We took the batch sizes that were used in \cite{de2018weighted} and \cite{beckham2017unimodal} as a reference, and we expanded the range on both sides.
		\item \textit{Link function}. Different link functions have been used for the POM at the last layer output: logit, probit and complementary log-log.
	\end{itemize}

	\section{Results}
	\label{sect:results}
	In this section, we present the results of the experiments. For each dataset, we show a table with the detailed experiments done training the model with each combination of parameters. Every parameter combination has been run five times. These tables show the mean value and the standard deviation of each metric across these five executions for the test set. These values are exposed using the format $\text{MEAN}_{(SD)}$.

@@

	\begin{table*}[!t]
		\caption{Diabetic Retinopathy results. BS stands for Batch Size, LF for link function and LR for Learning Rate.}
		\label{table:DRresults}
		\footnotesize
		\centering
		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c|c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{MSE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
			5 & c log-log & $10^{-2}$ & $0.414_{(0.057)}$ & $0.075_{(0.042)}$ & $0.177_{(0.023)}$ & $0.165_{(0.020)}$ & $0.556_{(0.057)}$ & $0.833_{(0.042)}$ & $0.968_{(0.011)}$ & $0.816_{(0.021)}$\\
			5 & c log-log & $10^{-3}$ & $0.534_{(0.027)}$ & $0.102_{(0.011)}$ & $0.137_{(0.006)}$ & $0.123_{(0.004)}$ & $0.658_{(0.015)}$ & $0.871_{(0.011)}$ & $0.966_{(0.003)}$ & $0.852_{(0.002)}$\\
			5 & c log-log & $10^{-4}$ & $0.520_{(0.006)}$ & $0.067_{(0.008)}$ & $0.123_{(0.003)}$ & $0.104_{(0.001)}$ & $0.697_{(0.006)}$ & $0.842_{(0.008)}$ & $0.961_{(0.003)}$ & $0.851_{(0.002)}$\\
			5 & logit & $10^{-2}$ & $0.416_{(0.041)}$ & $0.095_{(0.029)}$ & $0.175_{(0.021)}$ & $0.162_{(0.018)}$ & $0.563_{(0.054)}$ & $0.762_{(0.040)}$ & $0.908_{(0.026)}$ & $0.807_{(0.029)}$\\
			5 & logit & $10^{-3}$ & $0.554_{(0.013)}$ & $0.093_{(0.009)}$ & $0.137_{(0.003)}$ & $0.123_{(0.003)}$ & $0.660_{(0.008)}$ & $0.802_{(0.005)}$ & $0.936_{(0.004)}$ & $0.853_{(0.005)}$\\
			5 & logit & $10^{-4}$ & $0.520_{(0.003)}$ & $0.063_{(0.004)}$ & $0.122_{(0.002)}$ & $0.102_{(0.001)}$ & $0.706_{(0.005)}$ & $0.823_{(0.004)}$ & $0.949_{(0.003)}$ & $0.862_{(0.003)}$\\
			5 & probit & $10^{-2}$ & $0.460_{(0.048)}$ & $0.079_{(0.046)}$ & $0.197_{(0.064)}$ & $0.182_{(0.053)}$ & $0.504_{(0.167)}$ & $0.808_{(0.034)}$ & $0.927_{(0.073)}$ & $0.689_{(0.240)}$\\
			5 & probit & $10^{-3}$ & $0.564_{(0.018)}$ & $0.099_{(0.013)}$ & $0.147_{(0.018)}$ & $0.132_{(0.014)}$ & $0.636_{(0.045)}$ & $0.822_{(0.040)}$ & $0.939_{(0.020)}$ & $0.840_{(0.015)}$\\
			5 & probit & $10^{-4}$ & $0.523_{(0.005)}$ & $0.067_{(0.012)}$ & $0.122_{(0.002)}$ & $0.105_{(0.001)}$ & $0.701_{(0.006)}$ & $0.823_{(0.002)}$ & $0.953_{(0.002)}$ & $0.860_{(0.003)}$\\
			10 & c log-log & $10^{-2}$ & $0.423_{(0.239)}$ & $0.062_{(0.051)}$ & $0.127_{(0.017)}$ & $0.120_{(0.014)}$ & $0.684_{(0.046)}$ & $\mathbf{0.894_{(0.062)}}$ & $\mathbf{0.986_{(0.012)}}$ & $0.832_{(0.020)}$\\
			10 & c log-log & $10^{-3}$ & $\mathbf{0.582_{(0.016)}}$ & $0.102_{(0.006)}$ & $0.128_{(0.003)}$ & $0.115_{(0.002)}$ & $0.680_{(0.007)}$ & $\mathit{0.880_{(0.004)}}$ & $0.972_{(0.003)}$ & $0.861_{(0.004)}$\\
			10 & c log-log & $10^{-4}$ & $0.537_{(0.010)}$ & $0.064_{(0.004)}$ & $\mathit{0.116_{(0.001)}}$ & $0.096_{(0.001)}$ & $0.717_{(0.003)}$ & $0.837_{(0.002)}$ & $0.971_{(0.001)}$ & $0.860_{(0.002)}$\\
			10 & logit & $10^{-2}$ & $0.531_{(0.031)}$ & $0.107_{(0.008)}$ & $0.151_{(0.010)}$ & $0.140_{(0.008)}$ & $0.623_{(0.025)}$ & $0.802_{(0.022)}$ & $0.934_{(0.013)}$ & $0.838_{(0.014)}$\\
			10 & logit & $10^{-3}$ & $0.579_{(0.009)}$ & $0.096_{(0.012)}$ & $0.127_{(0.005)}$ & $0.113_{(0.004)}$ & $0.686_{(0.013)}$ & $0.817_{(0.006)}$ & $0.954_{(0.005)}$ & $0.861_{(0.002)}$\\
			10 & logit & $10^{-4}$ & $0.539_{(0.007)}$ & $0.074_{(0.013)}$ & $0.126_{(0.005)}$ & $0.095_{(0.002)}$ & $0.707_{(0.010)}$ & $0.823_{(0.007)}$ & $0.957_{(0.005)}$ & $0.858_{(0.004)}$\\
			10 & probit & $10^{-2}$ & $0.508_{(0.037)}$ & $0.088_{(0.044)}$ & $0.145_{(0.018)}$ & $0.137_{(0.014)}$ & $0.639_{(0.045)}$ & $0.835_{(0.015)}$ & $0.960_{(0.008)}$ & $0.829_{(0.020)}$\\
			10 & probit & $10^{-3}$ & $0.558_{(0.034)}$ & $\mathbf{0.111_{(0.005)}}$ & $0.134_{(0.003)}$ & $0.120_{(0.002)}$ & $0.666_{(0.008)}$ & $0.831_{(0.007)}$ & $0.955_{(0.001)}$ & $0.863_{(0.003)}$\\
			10 & probit & $10^{-4}$ & $0.541_{(0.010)}$ & $0.076_{(0.006)}$ & $0.119_{(0.002)}$ & $0.098_{(0.001)}$ & $0.712_{(0.005)}$ & $0.828_{(0.003)}$ & $0.961_{(0.002)}$ & $0.862_{(0.001)}$\\
			15 & c log-log & $10^{-2}$ & $0.564_{(0.016)}$ & $0.108_{(0.014)}$ & $0.143_{(0.006)}$ & $0.134_{(0.005)}$ & $0.640_{(0.015)}$ & $0.879_{(0.011)}$ & $0.972_{(0.005)}$ & $0.851_{(0.006)}$\\
			15 & c log-log & $10^{-3}$ & $0.559_{(0.026)}$ & $\mathit{0.111_{(0.008)}}$ & $0.127_{(0.004)}$ & $0.113_{(0.003)}$ & $0.682_{(0.010)}$ & $0.871_{(0.008)}$ & $\mathit{0.974_{(0.002)}}$ & $\mathbf{0.868_{(0.002)}}$\\
			15 & c log-log & $10^{-4}$ & $0.538_{(0.009)}$ & $0.054_{(0.003)}$ & $\mathbf{0.115_{(0.002)}}$ & $\mathit{0.093_{(0.001)}}$ & $0.720_{(0.006)}$ & $0.835_{(0.007)}$ & $0.970_{(0.003)}$ & $0.860_{(0.006)}$\\
			15 & logit & $10^{-2}$ & $0.551_{(0.020)}$ & $0.104_{(0.008)}$ & $0.139_{(0.011)}$ & $0.129_{(0.009)}$ & $0.654_{(0.027)}$ & $0.815_{(0.017)}$ & $0.948_{(0.016)}$ & $0.856_{(0.015)}$\\
			15 & logit & $10^{-3}$ & $0.551_{(0.010)}$ & $0.106_{(0.016)}$ & $0.129_{(0.008)}$ & $0.114_{(0.005)}$ & $0.680_{(0.019)}$ & $0.818_{(0.008)}$ & $0.952_{(0.007)}$ & $\mathit{0.866_{(0.001)}}$\\
			15 & logit & $10^{-4}$ & $0.543_{(0.008)}$ & $0.056_{(0.003)}$ & $0.121_{(0.004)}$ & $\mathbf{0.090_{(0.001)}}$ & $\mathbf{0.723_{(0.004)}}$ & $0.833_{(0.004)}$ & $0.964_{(0.003)}$ & $0.862_{(0.004)}$\\
			15 & probit & $10^{-2}$ & $0.534_{(0.032)}$ & $0.104_{(0.013)}$ & $0.148_{(0.015)}$ & $0.138_{(0.014)}$ & $0.631_{(0.038)}$ & $0.845_{(0.030)}$ & $0.964_{(0.010)}$ & $0.852_{(0.010)}$\\
			15 & probit & $10^{-3}$ & $\mathit{0.580_{(0.021)}}$ & $0.104_{(0.016)}$ & $0.129_{(0.008)}$ & $0.116_{(0.005)}$ & $0.680_{(0.018)}$ & $0.832_{(0.010)}$ & $0.959_{(0.007)}$ & $0.866_{(0.003)}$\\
			15 & probit & $10^{-4}$ & $0.533_{(0.004)}$ & $0.065_{(0.005)}$ & $0.117_{(0.002)}$ & $0.094_{(0.001)}$ & $\mathit{0.721_{(0.004)}}$ & $0.832_{(0.002)}$ & $0.964_{(0.001)}$ & $0.863_{(0.001)}$
		\end{tabular}
	\end{table*}

@@

	\subsection{Adience}
	\label{sect:adience}
	Results for the experiments made with the Adience dataset are shown in Table \ref{table:AdienceTest}.

	\begin{table*}[!t]
		\caption{Adience test results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
		\label{table:AdienceTest}
		\footnotesize
		\centering
		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c|c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{MSE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
			64 & c log-log & $10^{-2}$ & $0.808_{(0.025)}$ & $0.086_{(0.041)}$ & $0.147_{(0.008)}$ & $0.129_{(0.007)}$ & $0.415_{(0.031)}$ & $0.677_{(0.024)}$ & $0.798_{(0.036)}$ & $0.804_{(0.015)}$\\
			64 & c log-log & $10^{-3}$ & $0.873_{(0.006)}$ & $0.144_{(0.057)}$ & $\mathbf{0.124_{(0.003)}}$ & $0.101_{(0.003)}$ & $\mathbf{0.519_{(0.014)}}$ & $\mathit{0.764_{(0.010)}}$ & $0.861_{(0.019)}$ & $0.886_{(0.006)}$\\
			64 & c log-log & $10^{-4}$ & $0.799_{(0.010)}$ & $0.000_{(0.000)}$ & $0.174_{(0.001)}$ & $0.100_{(0.002)}$ & $0.324_{(0.015)}$ & $0.616_{(0.020)}$ & $0.795_{(0.012)}$ & $0.771_{(0.014)}$\\
			64 & logit & $10^{-2}$ & $0.778_{(0.019)}$ & $0.074_{(0.041)}$ & $0.159_{(0.006)}$ & $0.137_{(0.007)}$ & $0.366_{(0.025)}$ & $0.636_{(0.015)}$ & $0.785_{(0.010)}$ & $0.775_{(0.015)}$\\
			64 & logit & $10^{-3}$ & $\mathbf{0.881_{(0.005)}}$ & $\mathit{0.178_{(0.023)}}$ & $\mathit{0.126_{(0.001)}}$ & $0.098_{(0.003)}$ & $\mathit{0.518_{(0.008)}}$ & $\mathbf{0.765_{(0.015)}}$ & $\mathbf{0.902_{(0.005)}}$ & $\mathbf{0.894_{(0.005)}}$\\
			64 & logit & $10^{-4}$ & $0.784_{(0.011)}$ & $0.000_{(0.000)}$ & $0.180_{(0.001)}$ & $0.108_{(0.004)}$ & $0.318_{(0.026)}$ & $0.621_{(0.034)}$ & $0.772_{(0.024)}$ & $0.731_{(0.030)}$\\
			64 & probit & $10^{-2}$ & $0.836_{(0.005)}$ & $0.135_{(0.021)}$ & $0.134_{(0.002)}$ & $0.121_{(0.002)}$ & $0.468_{(0.011)}$ & $0.720_{(0.009)}$ & $0.861_{(0.009)}$ & $0.829_{(0.005)}$\\
			64 & probit & $10^{-3}$ & $\mathit{0.874_{(0.004)}}$ & $0.134_{(0.012)}$ & $0.126_{(0.003)}$ & $0.105_{(0.003)}$ & $0.511_{(0.014)}$ & $0.756_{(0.009)}$ & $\mathit{0.895_{(0.003)}}$ & $\mathit{0.889_{(0.003)}}$\\
			64 & probit & $10^{-4}$ & $0.805_{(0.004)}$ & $0.000_{(0.000)}$ & $0.170_{(0.001)}$ & $0.100_{(0.002)}$ & $0.360_{(0.011)}$ & $0.653_{(0.011)}$ & $0.809_{(0.009)}$ & $0.790_{(0.009)}$\\
			128 & c log-log & $10^{-2}$ & $0.832_{(0.013)}$ & $0.123_{(0.031)}$ & $0.135_{(0.004)}$ & $0.117_{(0.002)}$ & $0.463_{(0.013)}$ & $0.705_{(0.019)}$ & $0.813_{(0.025)}$ & $0.832_{(0.006)}$\\
			128 & c log-log & $10^{-3}$ & $0.873_{(0.006)}$ & $\mathbf{0.185_{(0.029)}}$ & $0.128_{(0.002)}$ & $0.100_{(0.001)}$ & $0.513_{(0.007)}$ & $0.758_{(0.008)}$ & $0.870_{(0.011)}$ & $0.880_{(0.009)}$\\
			128 & c log-log & $10^{-4}$ & $0.659_{(0.025)}$ & $0.000_{(0.000)}$ & $0.190_{(0.002)}$ & $0.125_{(0.004)}$ & $0.235_{(0.026)}$ & $0.466_{(0.031)}$ & $0.640_{(0.030)}$ & $0.536_{(0.041)}$\\
			128 & logit & $10^{-2}$ & $0.781_{(0.041)}$ & $0.096_{(0.059)}$ & $0.153_{(0.007)}$ & $0.125_{(0.007)}$ & $0.398_{(0.031)}$ & $0.638_{(0.033)}$ & $0.790_{(0.025)}$ & $0.779_{(0.020)}$\\
			128 & logit & $10^{-3}$ & $0.865_{(0.005)}$ & $0.127_{(0.026)}$ & $0.134_{(0.001)}$ & $0.099_{(0.003)}$ & $0.497_{(0.009)}$ & $0.754_{(0.008)}$ & $0.882_{(0.009)}$ & $0.874_{(0.008)}$\\
			128 & logit & $10^{-4}$ & $0.586_{(0.008)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.151_{(0.005)}$ & $0.192_{(0.001)}$ & $0.364_{(0.060)}$ & $0.581_{(0.034)}$ & $0.396_{(0.002)}$\\
			128 & probit & $10^{-2}$ & $0.849_{(0.005)}$ & $0.132_{(0.010)}$ & $0.131_{(0.001)}$ & $0.115_{(0.001)}$ & $0.479_{(0.004)}$ & $0.728_{(0.007)}$ & $0.854_{(0.009)}$ & $0.847_{(0.007)}$\\
			128 & probit & $10^{-3}$ & $0.866_{(0.002)}$ & $0.124_{(0.043)}$ & $0.130_{(0.002)}$ & $0.100_{(0.003)}$ & $0.505_{(0.006)}$ & $0.750_{(0.010)}$ & $0.882_{(0.004)}$ & $0.873_{(0.006)}$\\
			128 & probit & $10^{-4}$ & $0.718_{(0.015)}$ & $0.000_{(0.000)}$ & $0.185_{(0.001)}$ & $0.110_{(0.002)}$ & $0.300_{(0.031)}$ & $0.575_{(0.015)}$ & $0.733_{(0.010)}$ & $0.640_{(0.033)}$\\
			256 & c log-log & $10^{-2}$ & $0.853_{(0.004)}$ & $0.157_{(0.024)}$ & $0.130_{(0.002)}$ & $0.110_{(0.001)}$ & $0.485_{(0.009)}$ & $0.744_{(0.006)}$ & $0.842_{(0.016)}$ & $0.858_{(0.004)}$\\
			256 & c log-log & $10^{-3}$ & $0.840_{(0.017)}$ & $0.095_{(0.017)}$ & $0.144_{(0.005)}$ & $0.097_{(0.004)}$ & $0.456_{(0.021)}$ & $0.720_{(0.022)}$ & $0.840_{(0.018)}$ & $0.842_{(0.018)}$\\
			256 & c log-log & $10^{-4}$ & $0.552_{(0.010)}$ & $0.000_{(0.000)}$ & $0.199_{(0.001)}$ & $0.165_{(0.004)}$ & $0.187_{(0.001)}$ & $0.368_{(0.022)}$ & $0.475_{(0.025)}$ & $0.387_{(0.001)}$\\
			256 & logit & $10^{-2}$ & $0.764_{(0.102)}$ & $0.077_{(0.067)}$ & $0.155_{(0.020)}$ & $0.125_{(0.015)}$ & $0.387_{(0.083)}$ & $0.632_{(0.103)}$ & $0.790_{(0.077)}$ & $0.783_{(0.065)}$\\
			256 & logit & $10^{-3}$ & $0.851_{(0.008)}$ & $0.100_{(0.030)}$ & $0.147_{(0.003)}$ & $\mathbf{0.094_{(0.002)}}$ & $0.449_{(0.015)}$ & $0.726_{(0.015)}$ & $0.861_{(0.006)}$ & $0.850_{(0.008)}$\\
			256 & logit & $10^{-4}$ & $0.558_{(0.008)}$ & $0.000_{(0.000)}$ & $0.202_{(0.001)}$ & $0.191_{(0.002)}$ & $0.187_{(0.002)}$ & $0.206_{(0.007)}$ & $0.395_{(0.046)}$ & $0.389_{(0.003)}$\\
			256 & probit & $10^{-2}$ & $0.858_{(0.005)}$ & $0.164_{(0.033)}$ & $0.130_{(0.002)}$ & $0.112_{(0.002)}$ & $0.486_{(0.007)}$ & $0.741_{(0.008)}$ & $0.867_{(0.008)}$ & $0.862_{(0.005)}$\\
			256 & probit & $10^{-3}$ & $0.850_{(0.008)}$ & $0.111_{(0.040)}$ & $0.144_{(0.002)}$ & $\mathit{0.095_{(0.001)}}$ & $0.460_{(0.011)}$ & $0.732_{(0.006)}$ & $0.865_{(0.006)}$ & $0.853_{(0.007)}$\\
			256 & probit & $10^{-4}$ & $0.565_{(0.010)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.150_{(0.005)}$ & $0.189_{(0.001)}$ & $0.409_{(0.014)}$ & $0.602_{(0.022)}$ & $0.392_{(0.002)}$
		\end{tabular}
	\end{table*}
